### 2017-12-30 icde/revision/Response.tex

\textbf{Response to the comments of Referee 2.}

\textbf{[R2W1]} \emph{While practically the paper makes a good case about the particular application domain and its contributions there, the paper lacks technical depth.} \\
\textbf{[R2D1]} \emph{There seem to be two ``contradictory" sides to this paper. From one side, this is a great ``applications" paper where existing techniques and some good intuition is used to get better results into an existing (practical) problem. From a purely research and technical perspective, the paper is on the weak side. Pagerank and (incremental) versions of it already exist and the paper makes little contributions there. The claim (made twice) in the related work section that ``Different from previous work" this paper focuses on citations statistics doesn't hold water. The fact that the authors are considering a different application domain is not a contribution compared to past (incremental) pagerank papers. Unless there is a better claim to be made about the algorithmic side of the paper, as things stand, the paper makes minimal technical contributions.}

We thank the reviewer for appreciating the practice merit of our work which is drawn from an important and practical problem.

%And we believe this paper also stands from research and technique perspective.
And We think that the techniques proposed also have their own interests: a) An importance assembling based ranking model itself is hard to define and tune, b) an incremental algorithm for block-wise time-weighted PageRank computation that makes use of the particular properties of the scholarly graphs, and c) a thorough experimental study. That is, this paper certainly has its contributions to the technical part.

@@

Yes, we add the volume statistics (the number of articles published at each year) of the growing data  in Figure 1.

\textbf{[R3D3]} \emph{It is suggested that the authors should include some references to papers addressing the time delaying problem such as temporal graph, since it is related to the topic.}

Yes. We have discussed the correlation between our work and temporal graphs and included necessary references in Related Work.

%******************* meta-reviewer ***********************************************
\line(1,0){500}

\textbf{Response to the comments of META-REVIEWER.}

\textbf{[D1]} \emph{The reviewers see some merit in the approach, but they have also raised important concerns regarding the technical depth and novelty of the approach. In particular, the authors use known techniques for an application (scientific article ranking) for which there is abundance of previous work (it even has its own field, called scientometrics, or  bibliometrics).}

The techniques used in our work are not simply existing techniques:
a) an importance assembling based ranking model is still novel in the field of scientometrics and bibliometrics and we further consider the efficient batch and dynamic computation problem which rarely has been exploited in these two fields, b) an incremental algorithm for block-wise time-weighted PageRank computation that makes use of the particular properties of the scholarly graphs, and c) a thorough experimental study.
That is, although bearing similarities, this paper certainly has its contributions to the technical part and brings certain novelty for the task.

Please also refer to our response to R2W1\&D1 for more details.

### 2017-12-30 icde/revision/sec-exp.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t!]
%\vspace{-2ex}
\label{tab-result}
\begin{center}
\caption{\small Memory cost of algorithms}
%\begin{small}
\vspace{-.5ex}
\begin{tabular}{|c|c|c|c|c|}
\hline
{\bf Datasets}   &  \hspace{1ex}\pagerank\hspace{1ex}     & \hspace{1ex}\futurerank\hspace{1ex}  &  \hspace{1ex}\hhgrank\hspace{1ex}  &   \hspace{1ex}\ensemblerank\hspace{1ex}    \\
\hline \hline
\aan  & $0.671$   & $0.738$   & $0.758$     & {\bf 0.805}      \\  %\hline
\aminer  & $0.651$   & $0.729$   & $0.730$     & {\bf 0.778}      \\ %\hline
\magdata  & $0.615$   & $0.655$   & $0.658$     & {\bf 0.680}      \\ \hline
\end{tabular}
%\vspace{-.5ex}
%\end{small}
\end{center}
\vspace{-6ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

\stitle{Exp-4: Memory cost}.
In the fourth set of tests, we evaluated the memory cost of our algorithm. For a fair comparison, all algorithms used data before 2014, since the \hhgrank will run out of memory in 2015. The results of memory cost are reported in Table~IV.
The original data including
\markedb{The memory cost is an important factor of efficiency. We thus collect the memory use on the largest \magdata that (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB when $Y_s=2014$. Interestingly, our \ensemblerank model costs more memory than \futurerank due to its model complexity, while it is more efficient with our batch and incremental algorithms.}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t!]
%\vspace{-2ex}
\label{tab-result}
\begin{center}
\caption{\small Memory cost of algorithms}
%\begin{small}
\vspace{-.5ex}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
{\bf Datasets}   &  \hspace{1ex}Original\hspace{1ex}     &  \hspace{1ex}\pagerank\hspace{1ex}     & \hspace{1ex}\futurerank\hspace{1ex}  &  \hspace{1ex}\hhgrank\hspace{1ex}  &   \hspace{1ex}\ensemblerank\hspace{1ex}    \\
\hline \hline
\aan  & 6.80MB   & 5.03MB   & 5.86MB   & 11.06MB     & 13.09MB      \\  %\hline
\aminer  & 288.87MB   & 263.81MB   & 404.46MB   & 1.34GB     & 1.28GB      \\ %\hline
\magdata  & 10.46GB   & 8.67GB   & 14.32GB   & 61.37GB     & 48.13GB      \\ \hline
\end{tabular}
%\vspace{-.5ex}
%\end{small}
\end{center}
\vspace{-6ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

\stitle{Exp-4: Memory cost}.

In the fourth set of tests, we evaluated the memory cost of our algorithm. For a fair comparison, all algorithms used all data on both \aan and \aminer, and used data before 2014 on \magdata, since the \hhgrank will run out of memory in when $Y_s=2015$. The original data including paper citation graph, paper-author graph, paper-venue graph and time information of articles. The results of memory cost are reported in Table~IV.

For all algorithms, the memory cost increases with the original graph. Moreover, the more complexity the algorithm is, the more memory it costs. The memory cost of \pagerank is much lower than the one of other algorithms, since it only uses the citation information alone. Moreover, \ensemblerank costs more memory than \futurerank due to it also uses venue information besides of author information which \futurerank uses. The memory cost of \hhgrank is much higher than the one of other algorithms except on \aan possibly because the hypernetwork it generates will be more complicated with bigger original graph. Consider that, we choose to evaluate the prestige of an author with the average prestige of all articles published by the author instead of constructing an author citation graph with author component.
